%-------------------------
% Resume in LaTeX (Jake's Resume style)
% Author: Jiwon Jeong
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Jiwon Jeong} \\ \vspace{1pt}
    \small AI Research Engineer \\ \vspace{3pt}
    \small \faEnvelope\ \href{mailto:jwjw9603@gmail.com}{\underline{jwjw9603@gmail.com}} $|$
    \faGithub\ \href{https://github.com/jw9603}{\underline{github.com/jw9603}} $|$
    \faLinkedin\ \href{https://www.linkedin.com/in/jiwon-jeong-75951235b}{\underline{LinkedIn}} $|$
    \faIcon{robot}\ \href{https://huggingface.co/jiwon9703}{\underline{Hugging Face}} $|$
    \faGlobe\ \href{https://jw9603.github.io}{\underline{jw9603.github.io}}
\end{center}

%-----------RESEARCH INTERESTS-----------
\section{Research Interests}
  Reasoning in Large Language Models, Language-Mixed Chain-of-Thought, Bilingual Reasoning, Korean LLMs, Post-Training, LLM Evaluation

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sungkyunkwan University (SKKU)}{Suwon, South Korea}
      {M.S. in Artificial Intelligence}{Mar. 2022 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{Advisor: Prof. Hogun Park}
        \resumeItem{Research: Commonsense QA, Logical Fallacy Detection}
      \resumeItemListEnd

    \resumeSubheading
      {Kookmin University}{Seoul, South Korea}
      {B.S. in Electronic Engineering}{Mar. 2016 -- Feb. 2022}

  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Research Engineer}{Sep. 2025 -- Present}
      {Lotte Innovate -- AI Tech LAB, Language AI Team}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{AI Research Engineer responsible for LLM research and enterprise deployment}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TEACHING & MENTORING-----------
\section{Teaching \& Mentoring}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Online Mentor}{Feb. 2026}
      {LIKELION -- AI NLP Engineer Intensive Course, 3rd Cohort}{Remote}
      \resumeItemListStart
        \resumeItem{Mentored 4 teams on AI-based service development projects using corporate and public data}
        \resumeItem{Provided code review, project coaching, and Q\&A support via Discord}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{2023 -- 2024}
      {Sungkyunkwan University}{Suwon, South Korea}
      \resumeItemListStart
        \resumeItem{TA for Language Model course (SWE3032-41) and Deep Learning advanced courses for non-CS educators}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACTIVITIES-----------
\section{Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Runner -- ``Deep Dive into LLM''}{Mar. 2026 -- Present}
      {Pseudo-Lab (\href{https://pseudo-lab.com/projects/ac9d57ad-630c-4d86-b8fe-615c0b5ed7c6}{\underline{link}}) -- Non-profit AI research community}{Remote}
      \resumeItemListStart
        \resumeItem{Studying Stanford CS336: Language Modeling from Scratch (2026) through weekly online discussions}
        \resumeItem{Research project to be selected and pursued after course completion}
      \resumeItemListEnd

    \resumeSubheading
      {AI Researcher}{Aug. 2025 -- Jan. 2026}
      {B-Peach LAB (Tech for Impact)}{Remote}
      \resumeItemListStart
        \resumeItem{Designed evaluation metrics for AI-powered text adaptation service improving information accessibility for slow learners}
        \resumeItem{Conducted research on adaptation quality assessment}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{NAACL 2025 Findings}}{2025}
      \resumeItemListStart
        \resumeItem{Large Language Models Are Better Logical Fallacy Reasoners with Counterargument, Explanation, and Goal-Aware Prompt Formulation}
        \resumeItem{\textbf{Jiwon Jeong}, Hyeju Jang, Hogun Park}
        \resumeItem{\href{https://arxiv.org/abs/2503.23363}{\underline{arXiv}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{KSC 2022} $|$ \emph{Outstanding Paper Award (Top 10\%)}}{2022}
      \resumeItemListStart
        \resumeItem{Improving Commonsense-based QA Model through a Cycle-Encoder}
        \resumeItem{\textbf{Jiwon Jeong}, Soyoung Lee, Hogun Park}
        \resumeItem{\href{https://www.dbpia.co.kr/journal/articleDetail?nodeId=NODE11224246}{\underline{DBpia}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Open Source Contribution: Hugging Face Transformers} $|$ \emph{Python, Transformers}}{Mar. 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Removed six dead beam-search dummy classes left over from v5 cleanup, fixing a repository consistency check failure on PyTorch-less installs (\href{https://github.com/huggingface/transformers/pull/45722}{\underline{PR \#45722}}, merged Apr. 2026)}
        \resumeItem{Reported and fixed a protobuf decode error masking bug in tokenizer loading (\href{https://github.com/huggingface/transformers/pull/45486}{\underline{PR \#45486}}, merged Apr. 2026)}
        \resumeItem{Fixed a bug in continuous batching for multimodal models. Added input preprocessing and fallback mechanism for non-text-only models (\href{https://github.com/huggingface/transformers/pull/44436}{\underline{PR \#44436}}, merged Mar. 2026)}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{MCP Server for ChatGPT Apps} $|$ \emph{Python, FastAPI, MCP}}{Jan. 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Built MCP (Model Context Protocol) servers for ChatGPT Apps (OpenAI)}
        \resumeItem{Designed middleware architecture connecting frontend, backend, and LLM-powered enterprise solutions}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{B-Peach LAB -- Text Adaptation Service} $|$ \emph{NLP, Evaluation}}{Aug. 2025 -- Jan. 2026}
      \resumeItemListStart
        \resumeItem{Designed evaluation metrics for AI-powered text adaptation service for slow learners}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Korean LLM Benchmark} $|$ \emph{Python, LLM, Evaluation}}{Dec. 2025 -- Jan. 2026}
      \resumeItemListStart
        \resumeItem{Evaluation framework for Korean LLM performance with standardized metrics and reproducible pipelines}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{KSC 2022 Outstanding Paper Award} $|$ \emph{Top 10\% of accepted papers}}{2022}
    \resumeProjectHeading
      {\textbf{Text Ethics Hackathon -- 2nd Place}}{Nov. 2021 -- Dec. 2021}
      \resumeItemListStart
        \resumeItem{Developed ELECTRA-based classification model for detecting hate speech and biased text}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python} \\
     \textbf{Frameworks}{: PyTorch, Hugging Face Transformers, FastAPI, LangChain, Docker} \\
     \textbf{Research}{: NLP, LLM Fine-tuning, Prompt Engineering, Model Evaluation, MCP} \\
     \textbf{Tools}{: Git, Linux, Weights \& Biases, Jupyter}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
